Disclosure of Product System Models in Life Cycle Assessment: Achieving Transparency and Privacy

### 2018-02-08 revision/rev2-response.tex
response minor edits

Thank you again to the reviewers for their robust reading of my revised manuscript.  I appreciate that all reviewers found the article to be engaging and important.  Their comments helped me to clarify the presentation of the methodology and to improve the connection to current scholarship, notably Majeau-Bettez et al (2014).  I have taken all of the reviewers' recommendations to heart.  Below I respond to each individually.

@@

Regarding the computational efficiency of iteration vs inversion, I agree that the performance aspects are out of scope for the current paper.  However, the reviewer should note that in fact the Leontief inverse is the standard.  SimaPro, the leading worldwide software system for scientific LCA, converted to using an iterative Leontief inverse for Version 8, as disclosed in a whitepaper published in 2014 (https://www.pre-sustainability.com/news/new-calculation-engine-simapro-8), realizing significant speed and memory usage improvements.  OpenLCA, the open-source alternative, also reported a dramatic reduction in memory usage and computation time around the release of version 1.4 in 2014, coincident with a revised algorithm "optimized for huge databases" (http://www.openlca.org/openlca-beta-1-4-released-optimised-for-huge-databases/) which is highly suggestive of a switch to an iterative approach.  GaBi, the more industrially oriented alternative, does not use a matrix formulation at all, but has always computed activity levels using iteration at the plan level.

>>>>

Thank you again to the reviewers for their robust reading of my revised manuscript.  I appreciate that all reviewers found the article to be engaging and important.  Their comments helped me to clarify the presentation of the methodology and to improve the connection to current scholarship, notably Majeau-Bettez et al (2014).

I have taken all of the reviewers' recommendations to heart.  The major changes to the manuscript were in the mathematical introduction sections-- I have rewritten ``Mathematical Formulation of LCA'' to centralize the supply-and-use framework, and to emphasize that the matrices developed in the text are coefficient matrices derived from supply and use tables.  I have also rewritten ``Foreground Study'' to better illustrate how a foreground study is constructed with reference to a background database, and to better define the canonical functional unit.  I added a new figure at the request of Reviewer \#3, and a new discussion subsection dealing with the role of the community.  I also made an assortment of clarifying changes throughout the document.

Below I respond to each comment individually.

@@

Regarding the computational efficiency of iteration vs inversion, I agree that the performance aspects are out of scope for the current paper.  However, the reviewer should note that in fact the Leontief inverse is the standard.  SimaPro, the leading worldwide software system for scientific LCA, converted to using an iterative Leontief inverse for Version 8, as disclosed in a whitepaper published in 2014 (https://www.pre-sustainability.com/news/new-calculation-engine-simapro-8), realizing significant speed and memory usage improvements.  OpenLCA, the open-source alternative, also reported a dramatic reduction in memory usage and computation time around the release of version 1.4 in 2014, coincident with a revised algorithm "optimized for huge databases" (http://www.openlca.org/openlca-beta-1-4-released-optimised-for-huge-databases/). This is highly suggestive of a switch to an iterative approach.  GaBi, the more industrially oriented software, does not use a matrix formulation at all, but has always computed activity levels using iteration at the plan level.
